\LARGE{\bf{Natural variation in teosinte at the domestication locus \emph{teosinte branched1} (\emph{tb1})}}\footnotemark

### 2014-05-29 Supplement_mbh.tex
New supplement edited
final formatting for supplement

%Note that if authors wish to submit long DNA sequence appendices as supplemental material, they should select the "DNA sequences (online-only supplemental)" option on Editorial Manager. This ensures that lengthy appendices are not built into the reviewers' PDF, but are still accessible to the reviewers.
\documentclass[11pt]{article}
\usepackage{geometry} 
\usepackage{hyperref}
\usepackage[leftcaption]{sidecap}
\sidecaptionvpos{figure}{c} %position side caption
\usepackage{lineno}
\usepackage{lipsum}
\usepackage{indentfirst}
\usepackage{color}
\usepackage{multirow}
\usepackage[utf8]{inputenc}
\usepackage{array}
	\newcounter{rowno}
	\setcounter{rowno}{0}
\usepackage{booktabs}
\usepackage[pdftex]{graphicx}  
\usepackage{caption}
\usepackage{natbib}
\usepackage{authblk}
\usepackage[table]{xcolor} %for table line color alteration
\usepackage{subscript}
\usepackage{longtable}

@@

% Figure S1. Cartoon representation of tb1 locus
%-------------------------------------------------------------------
\begin{figure*}[!t]
  \begin{center}
   \includegraphics[width=140mm]{FigS1LocusCartoon.pdf}
   \caption{Representation of the upstream regulatory region of \emph{tb1}, showing the \emph{tb1} coding region (green) and the \emph{Hopscotch} insertion (red). Arrows show the location of primer sets; in black, primers used for amplification and sequencing (Sequenced region 1; within the 5' UTR, and sequenced region 2; 66,169 bp upstream from the tb1 ORF); in blue, primers used to genotype the \emph{Hopscotch} insertion.}
  \end{center}
\end{figure*}
%-------------------------------------------------------------------

% Figure S2. Gel image
%-------------------------------------------------------------------
\begin{figure*}[!t]
  \begin{center}
   \includegraphics[width=100mm]{FigS2Gel.png}
   \caption{Agarose gel image of amplification products using our primer sets. Genotypes are indicated at the top of the gel.} 
  \end{center}
\end{figure*}
%-------------------------------------------------------------------

% Figure S3. NJ Trees
%-------------------------------------------------------------------
\begin{figure*}[!t]
  \begin{center}
   \includegraphics[width=100mm]{FigS3NJtrees.pdf}
    \caption{Neighbor-Joining tree of the sequenced region in the 5? UTR (right; sequenced region 1) and the 66,169 bp upstream region (left; sequenced region 2) of \emph{tb1}. Individuals with genotype data are colored: Homozygous for the teosinte (no \emph{Hopscotch}) allele (red), homozygous for the maize (\emph{Hopscotch}) allele (blue), heterozygotes (purple). TILs (teosinte inbred lines) are colored in green, with stars indicating the 3 TILs known to have the \emph{Hopscotch} insertion. Black indicates individuals not genotyped for the \emph{Hopscotch} insertion.} 
  \end{center}
\end{figure*}
%-------------------------------------------------------------------

% Table S1
\begin{table}[htbp]
\rowcolors{2}{gray!25}{white}
  \centering
  \caption{Pairwise F\textsubscript{ST} values from sequence and \emph{Hopscotch} genotyping data}

    \begin{tabular}{cccc}\\\toprule
    \textbf{Comparison} & \textbf{Region 1} & \textbf{Region 2} & \textbf{\emph{Hopscotch}} \\\midrule
    EjuA \& EjuB & 0     & 0     & 0 \\
    EjuA \& MSA & 0.326 & 0.328 & 0.186 \\
    EjuA \& SLO & 0.416 & 0.258 & 0.280 \\
    EjuB \& MSA & 0.397 & 0.365 & 0.188 \\
    EjuB \& SLO & 0.512  & 0.290 & 0.280 \\
    MSA \& SLO & 0.007  & 0 & 0.016 \\\bottomrule
    \end{tabular}
\end{table}

% Table S2. Parv and mex samples 
\begin{scriptsize}  % Switch from 12pt to 11pt; otherwise, table won't fit
\rowcolors{1}{gray!25}{white}
\begin{longtable}{>{\stepcounter{rowno}}cccccc}
\hiderowcolors
\caption{Accessions of \emph{Zea mays} ssp. \emph{mexicana} (RIMME) and \emph{Zea mays} ssp. \emph{parviglumis} (RIMPA) sampled. RIHY is a \emph{Z. mays} ssp. 	\emph{parviglumis} and \emph{Zea mays} ssp. \emph{mays} hybrid.}\\
\hline
\multicolumn{1}{c}{\textbf{Accession}} & \multicolumn{1}{c}{\textbf{USDA ID}} & \multicolumn{1}{c}{\textbf{Locality}} & \multicolumn{1}{c}{\textbf{Alleles Sampled}} & \multicolumn{1}{c}{\textbf{\emph{Hopscotch} Freq.}} & \multicolumn{1}{c}{\textbf{No \emph{Hopscotch} Freq.}} \\
\hline
\endhead
\showrowcolors

@@

@@

% Table S2. Mays sampling
\begin{table}[htbp]
\tiny
\rowcolors{2}{gray!25}{white}
  \centering
 \caption{\emph{Zea mays} ssp. \emph{mays} (RIMMA) sampled for genotyping}
    \begin{tabular}{ccc}
 %   \toprule
    Accession & Alleles Sampled & \emph{Hopscotch} Freq. \\
 %   \midrule

@@

    \bottomrule
    \end{tabular}
\end{table}

% Table S4. PCs for BayEnv
\begin{table}[htbp]
  \centering
  \caption{Variables and rotations used for the 6 principal components used for BayEnv calculations and their corresponding Bayes Factors. Modified from \citet{Pyhajarvi2013}.}
    \begin{tabular}{rrrrrrrrrrrr}
    \toprule
    \textbf{PC1} & \textbf{} & \textbf{PC2} & \textbf{} & \textbf{PC3} & \textbf{} & \textbf{PC4} & \textbf{} & \textbf{PC5} & \textbf{} & \textbf{PC6} & \textbf{} \\
    \midrule
    \textbf{Var} & \textbf{Rot} & \textbf{Var} & \textbf{Rot} & \textbf{Var} & \textbf{Rot} & \textbf{Var} & \textbf{Rot} & \textbf{Var} & \textbf{Rot} & \textbf{Var} & \textbf{Rot} \\
    bio1  & 0.146 & bio4  & 0.244 & prec7 & 0.287 & ts\_clay & 0.41  & bio2  & 0.38  & bio2  & 0.412 \\
    tmean11 & 0.146 & bio3  & 0.241 & prec8 & 0.276 & v\_mod & 0.359 & sq4   & 0.328 & x\_mod & 0.365 \\
    tmean12 & 0.145 & bio7  & 0.241 & prec11 & 0.262 & ts\_sand & 0.329 & ts\_loam & 0.289 & sq7   & 0.332 \\
    bio11 & 0.145 & prec6 & 0.237 & bio13 & 0.247 & bio15 & 0.272 & ts\_sand & 0.266 & bio7  & 0.312 \\
    tmax12 & 0.145 & sq7   & 0.218 & prec1 & 0.246 & prec4 & 0.259 & sq7   & 0.231 & v\_mod & 0.307 \\
    tmin5 & 0.145 & prec9 & 0.217 & bio16 & 0.242 & x\_mod & 0.244 & bio18 & 0.213 & prec11 & 0.23 \\
    tmean1 & 0.145 & sq3   & 0.207 & prec12 & 0.24  & prec3 & 0.226 & bio13 & 0.207 & bio18 & 0.22 \\
    tmean2 & 0.145 & prec12 & 0.207 & bio19 & 0.238 & sq3   & 0.21  & prec11 & 0.183 & sq3   & 0.176 \\
    tmin4 & 0.145 & bio12 & 0.204 & bio12 & 0.231 & prec5 & 0.21  & bio7  & 0.17  & sq4   & 0.153 \\
    tmax1 & 0.145 & bio19 & 0.196 & prec2 & 0.222 & prec7 & 0.19  & bio16 & 0.163 & ts\_sand & 0.153 \\
    tmean4 & 0.145 & prec2 & 0.188 & bio18 & 0.221 & sq4   & 0.186 & bio4  & 0.157 & bio4  & 0.148 \\
    tmin11 & 0.144 & prec1 & 0.185 & sq4   & 0.2   & bio3  & 0.185 & bio12 & 0.156 & prec7 & 0.139 \\
    tmax11 & 0.144 & prec10 & 0.184 & prec9 & 0.18  & bio18 & 0.178 & bio3  & 0.155 & tmax3 & 0.127 \\
    tmin12 & 0.144 & bio16 & 0.183 & prec10 & 0.171 & sq7   & 0.132 & prec6 & 0.154 & tmax4 & 0.126 \\
    tmin2 & 0.144 & prec8 & 0.17  & prec5 & 0.161 & bio14 & 0.116 & x\_mod & 0.152 & bio5  & 0.118 \\
    tmean5 & 0.144 & prec5 & 0.165 & prec4 & 0.154 & bio13 & 0.099 & prec9 & 0.144 & tmax5 & 0.115 \\
    tmean10 & 0.144 & bio14 & 0.158 & sq3   & 0.147 & bio16 & 0.095 & prec8 & 0.143 & bio3  & 0.107 \\
    bio6  & 0.144 & bio13 & 0.151 & bio2  & 0.143 & prec8 & 0.09  & v\_mod & 0.142 & ts\_loam & 0.095 \\
    tmax2 & 0.144 & bio17 & 0.149 & bio17 & 0.129 & bio7  & 0.077 & bio15 & 0.136 & ts\_clay & 0.078 \\
    tmean3 & 0.144 & prec3 & 0.144 & ts\_loam & 0.127 & bio4  & 0.075 & prec7 & 0.112 & tmin9 & 0.072 \\
    tmin1 & 0.143 & ts\_clay & 0.141 & v\_mod & 0.123 & bio2  & 0.074 & prec4 & 0.108 & tmin8 & 0.071 \\
    tmin10 & 0.143 & bio2  & 0.129 & prec3 & 0.113 & prec2 & 0.074 & bio14 & 0.096 & prec9 & 0.07 \\
    Altitude & 0.143 & prec7 & 0.108 & x\_mod & 0.111 & bio19 & 0.068 & tmax7 & 0.093 & tmin10 & 0.069 \\
    bio9  & 0.143 & tmax6 & 0.107 & bio14 & 0.099 & prec12 & 0.056 & tmax8 & 0.092 & tmin12 & 0.069 \\
    tmin3 & 0.143 & x\_mod & 0.106 & bio4  & 0.07  & ts\_loam & 0.053 & prec1 & 0.091 & tmin7 & 0.066 \\
    bio10 & 0.142 & bio15 & 0.098 & tmax3 & 0.067 & tmax12 & 0.047 & prec2 & 0.086 & tmean4 & 0.066 \\
    tmax10 & 0.142 & ts\_loam & 0.088 & ts\_clay & 0.065 & bio17 & 0.047 & tmin11 & 0.086 & tmax2 & 0.066 \\
    tmax3 & 0.142 & tmean6 & 0.085 & bio15 & 0.056 & bio9  & 0.043 & prec5 & 0.082 & tmax6 & 0.064 \\
    tmax4 & 0.142 & tmin7 & 0.082 & tmax2 & 0.055 & tmax8 & 0.042 & bio17 & 0.082 & tmean3 & 0.064 \\
    tmin6 & 0.142 & bio5  & 0.082 & tmean3 & 0.052 & tmax1 & 0.041 & tmin12 & 0.08  & bio9  & 0.058 \\
    tmean9 & 0.141 & tmean7 & 0.081 & ts\_sand & 0.05  & tmax5 & 0.039 & prec3 & 0.078 & tmin11 & 0.058 \\
    tmin9 & 0.141 & prec4 & 0.08  & prec6 & 0.048 & tmax7 & 0.039 & tmax9 & 0.078 & prec3 & 0.056 \\
    tmean8 & 0.141 & tmax7 & 0.079 & sq7   & 0.048 & prec10 & 0.038 & tmin1 & 0.077 & tmean5 & 0.056 \\
    bio8  & 0.14  & bio8  & 0.079 & tmin7 & 0.046 & Altitude & 0.037 & tmin10 & 0.074 & bio10 & 0.051 \\
    tmean6 & 0.14  & tmax9 & 0.077 & bio3  & 0.044 & tmax10 & 0.035 & bio6  & 0.071 & bio15 & 0.047 \\
    tmean7 & 0.14  & tmean8 & 0.076 & tmax4 & 0.043 & tmax2 & 0.033 & prec12 & 0.067 & tmin1 & 0.045 \\
    tmin8 & 0.14  & tmin8 & 0.076 & bio7  & 0.042 & tmax9 & 0.03  & tmin2 & 0.061 & prec12 & 0.045 \\
    tmax5 & 0.14  & tmax5 & 0.074 & tmax1 & 0.036 & tmean12 & 0.029 & tmin6 & 0.061 & bio17 & 0.045 \\
    tmax9 & 0.139 & tmax8 & 0.074 & tmin3 & 0.035 & tmax11 & 0.027 & tmax6 & 0.059 & tmean10 & 0.043 \\
    tmax8 & 0.139 & tmean9 & 0.072 & bio9  & 0.035 & tmean1 & 0.027 & tmin3 & 0.052 & prec4 & 0.043 \\
    bio5  & 0.139 & bio18 & 0.07  & tmin8 & 0.034 & bio5  & 0.026 & bio8  & 0.046 & Altitude & 0.041 \\
    tmax7 & 0.139 & v\_mod & 0.066 & tmean4 & 0.031 & tmean5 & 0.026 & tmean11 & 0.041 & bio6  & 0.039 \\
    tmin7 & 0.138 & tmin9 & 0.066 & tmean2 & 0.031 & bio11 & 0.025 & tmean1 & 0.04  & tmin6 & 0.038 \\
    tmax6 & 0.135 & bio10 & 0.065 & tmax12 & 0.03  & tmean2 & 0.022 & tmin9 & 0.04  & tmean12 & 0.035 \\
    bio17 & 0.107 & tmax10 & 0.063 & tmean7 & 0.028 & tmin6 & 0.022 & tmean12 & 0.04  & tmean9 & 0.035 \\
    bio14 & 0.095 & tmin6 & 0.061 & tmin9 & 0.023 & prec1 & 0.022 & tmax10 & 0.038 & prec5 & 0.033 \\
    prec3 & 0.094 & prec11 & 0.056 & Altitude & 0.021 & tmean7 & 0.02  & tmin5 & 0.038 & tmean8 & 0.03 \\
    bio15 & 0.092 & ts\_sand & 0.054 & tmax11 & 0.019 & tmean8 & 0.02  & bio11 & 0.037 & tmin2 & 0.03 \\
    prec4 & 0.088 & sq4   & 0.049 & tmin4 & 0.018 & tmean9 & 0.019 & tmean8 & 0.035 & tmax1 & 0.03 \\
    prec10 & 0.084 & tmin3 & 0.048 & tmax5 & 0.017 & prec11 & 0.019 & tmean7 & 0.033 & prec1 & 0.025 \\
    ts\_sand & 0.073 & tmean10 & 0.047 & tmin10 & 0.017 & tmean11 & 0.018 & tmean2 & 0.03  & bio13 & 0.024 \\
    ts\_loam & 0.072 & tmean5 & 0.044 & tmin6 & 0.017 & tmax4 & 0.016 & bio19 & 0.029 & tmean11 & 0.023 \\
    prec6 & 0.069 & tmax4 & 0.042 & tmean6 & 0.017 & tmean10 & 0.016 & bio9  & 0.027 & tmax7 & 0.023 \\
    prec9 & 0.063 & tmax11 & 0.041 & tmax6 & 0.017 & tmin5 & 0.015 & tmin7 & 0.026 & tmean7 & 0.023 \\
    prec2 & 0.063 & bio6  & 0.038 & tmin12 & 0.017 & tmean6 & 0.015 & tmin4 & 0.025 & prec10 & 0.022 \\
    bio4  & 0.06  & tmin1 & 0.038 & bio11 & 0.016 & prec6 & 0.014 & tmean5 & 0.023 & prec2 & 0.02 \\
    prec5 & 0.058 & tmin2 & 0.037 & tmin11 & 0.015 & bio6  & 0.012 & tmean3 & 0.022 & bio8  & 0.018 \\
    bio13 & 0.055 & Altitude & 0.036 & tmin1 & 0.013 & tmin1 & 0.012 & tmin8 & 0.022 & tmean2 & 0.017 \\
    x\_mod & 0.053 & tmin10 & 0.034 & tmean5 & 0.013 & tmin12 & 0.011 & tmean10 & 0.021 & bio16 & 0.016 \\
    prec1 & 0.05  & bio9  & 0.032 & tmean8 & 0.013 & tmin2 & 0.011 & tmean9 & 0.019 & tmean6 & 0.014 \\
    bio16 & 0.049 & tmean1 & 0.029 & bio6  & 0.012 & bio1  & 0.011 & tmean4 & 0.019 & bio19 & 0.012 \\
    bio7  & 0.043 & bio1  & 0.028 & tmean9 & 0.01  & tmin4 & 0.009 & ts\_clay & 0.018 & tmax11 & 0.012 \\
    bio19 & 0.042 & tmean3 & 0.026 & tmean1 & 0.01  & tmax6 & 0.008 & prec10 & 0.015 & tmax10 & 0.011 \\
    bio12 & 0.042 & tmean2 & 0.024 & bio10 & 0.01  & tmin11 & 0.007 & bio1  & 0.014 & tmax8 & 0.01 \\
    bio3  & 0.04  & bio11 & 0.022 & tmax8 & 0.009 & bio8  & 0.007 & tmax4 & 0.014 & tmean1 & 0.009 \\
    prec7 & 0.034 & tmean11 & 0.019 & tmax7 & 0.009 & bio10 & 0.007 & bio10 & 0.011 & bio14 & 0.009 \\
    prec12 & 0.033 & tmin12 & 0.019 & bio5  & 0.008 & tmin9 & 0.006 & tmax5 & 0.009 & prec8 & 0.007 \\
    bio2  & 0.033 & tmax1 & 0.017 & tmin5 & 0.008 & prec9 & 0.005 & bio5  & 0.008 & bio11 & 0.007 \\
    prec8 & 0.032 & tmean4 & 0.016 & tmin2 & 0.007 & bio12 & 0.004 & tmax11 & 0.008 & tmin5 & 0.006 \\
    sq4   & 0.026 & tmin5 & 0.013 & bio1  & 0.007 & tmax3 & 0.003 & tmax12 & 0.008 & tmax9 & 0.005 \\
    sq3   & 0.024 & tmean12 & 0.012 & tmax10 & 0.006 & tmean4 & 0.003 & tmax3 & 0.007 & bio12 & 0.004 \\
    v\_mod & 0.015 & tmax2 & 0.011 & tmean10 & 0.006 & tmin3 & 0.002 & sq3   & 0.007 & tmin3 & 0.004 \\
    ts\_clay & 0.012 & tmin4 & 0.01  & tmean12 & 0.005 & tmin7 & 0.002 & tmax2 & 0.006 & prec6 & 0.004 \\
    sq7   & 0.004 & tmax3 & 0.003 & bio8  & 0.004 & tmean3 & 0.002 & Altitude & 0.004 & tmin4 & 0.003 \\
    prec11 & 0.004 & tmax12 & 0.002 & tmax9 & 0.003 & tmin10 & 0.002 & tmean6 & 0.002 & bio1  & 0.002 \\
    bio18 & 0.001 & tmin11 & 0.001 & tmean11 & 0.001 & tmin8 & 0     & tmax1 & 0.001 & tmax12 & 0.002 \\
    \textbf{Bayes Factors} &       &       &       &       &       &       &       &       &       &       &  \\
    \multicolumn{2}{c}{0.77165} & \multicolumn{2}{c}{0.51652} & \multicolumn{2}{c}{0.21120} & \multicolumn{2}{c}{0.24063} & \multicolumn{2}{c}{1.96010} & \multicolumn{2}{c}{0.24594} \\
    \bottomrule
    \end{tabular}%
\end{table}%

% Table S4 Diversity stats in tb1 region based on SNP 50 genotyping data
\begin{table}[htbp]
  \centering
  \caption{Diversity in the \emph{tb1} region based on the maize SNP50 genotyping data}
    \begin{tabular}{ccccc}\\
    \textbf{Population} & \textbf{\# Seg Sites} & \textbf{$\hat\theta_\pi)$ / bp} & \textbf{$\hat\theta_W$ / bp} & \textbf{Tajima's D} \\
    \midrule
    Ejutla A & 4     & 0.15217 & 0.11902 & 0.76191 \\
    Ejutla B & 5     & 0.15258 & 0.14877 & 0.07412 \\
    La Mesa & 3     & 0.12802 & 0.08926 & 1.09209 \\
    San Lorenzo & 3     & 0.09098 & 0.08926 & 0.04845 \\
    \bottomrule
    \end{tabular}%
\end{table}%
\end{document}

>>>>

%Note that if authors wish to submit long DNA sequence appendices as supplemental material, they should select the "DNA sequences (online-only supplemental)" option on Editorial Manager. This ensures that lengthy appendices are not built into the reviewers' PDF, but are still accessible to the reviewers.
\documentclass[11pt]{article}
\usepackage[letterpaper, margin=1in]{geometry} 
\usepackage{hyperref}
\usepackage[leftcaption]{sidecap}
\sidecaptionvpos{figure}{c} %position side caption
\usepackage{lineno}
\usepackage{lipsum}
\usepackage{indentfirst}
\usepackage{pdflscape}
\usepackage{color}
\usepackage{multirow}
\usepackage[utf8]{inputenc}
\usepackage{array}
	\newcounter{rowno}
	\setcounter{rowno}{0}
\usepackage{booktabs}
\usepackage[pdftex]{graphicx}  
\usepackage{caption}
\usepackage{natbib}
\usepackage{authblk}
\usepackage[table]{xcolor} %for table line color alteration
\usepackage{subscript}
\usepackage{longtable}
\usepackage{fancyhdr}
	\renewcommand{\headrulewidth}{0pt}
	\rfoot{\thepage}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\cfoot{\thepage}

\pagestyle{fancy}

@@

\chead{\small{Vann et al.---American Journal of Botany (\#\#)(\#): \#\#\#-\#\#\#. 2014. -- Appendix S1 -- Page \thepage}}

\centering{Appendix S1: Accessions of \emph{Zea mays} ssp. \emph{mexicana} (RIMME) and \emph{Zea mays} ssp. \emph{parviglumis} (RIMPA) sampled. RIHY is a \emph{Z. mays} ssp. \emph{parviglumis} and \emph{Zea mays} ssp. \emph{mays} hybrid.}

% Appendix S1. Parv and mex samples 
\begin{scriptsize}  % Switch from 12pt to 11pt; otherwise, table won't fit
\rowcolors{1}{gray!25}{white}
\begin{longtable}{>{\stepcounter{rowno}}cccccc}
\hiderowcolors
\hline
\multicolumn{1}{c}{\textbf{Accession}} & \multicolumn{1}{c}{\textbf{USDA ID}} & \multicolumn{1}{c}{\textbf{Locality}} & \multicolumn{1}{c}{\textbf{Alleles Sampled}} & \multicolumn{1}{c}{\textbf{\emph{Hopscotch} Freq.}} & \multicolumn{1}{c}{\textbf{No \emph{Hopscotch} Freq.}} \\
\hline
\endhead
\showrowcolors

@@

    \hline

@@

\pagenumbering{arabic}
\chead{\small{Vann et al.---American Journal of Botany (\#\#)(\#): \#\#\#-\#\#\#. 2014. -- Appendix S2 -- Page \thepage}}
% Appendix S2. Mays sampling

\centering{Appendix S2: \emph{Hopscotch} frequency in sampled \emph{Zea mays} ssp. \emph{mays} (RIMMA).}

\begin{scriptsize}  % Switch from 12pt to 11pt; otherwise, table won't fit
\rowcolors{1}{gray!25}{white}
\begin{longtable}{>{\stepcounter{rowno}}ccc}
\hiderowcolors
\hline
\multicolumn{1}{c}{\textbf{Accession}} & \multicolumn{1}{c}{\textbf{Alleles Sampled}} & \multicolumn{1}{c}{\textbf{\emph{Hopscotch} Freq.}} \\
\hline
\endhead
\showrowcolors

@@

    \hline

\clearpage
\pagenumbering{arabic}
\chead{\small{Vann et al.---American Journal of Botany (\#\#)(\#): \#\#\#-\#\#\#. 2014. -- Appendix S3 -- Page \thepage}}
% Appendix S3. Cartoon representation of tb1 locus
%-------------------------------------------------------------------
\begin{figure*}[!t]
  \begin{center}
   \includegraphics[width=180mm]{FigS1LocusCartoon.pdf}
   \flushleft{Appendix S3: Representation of the upstream regulatory region of \emph{tb1}, showing the \emph{tb1} coding region (green) and the \emph{Hopscotch} insertion (red). Arrows show the location of primer sets; in black, primers used for amplification and sequencing (Region 1; within the 5' UTR, and Region 2; 66,169 bp upstream from the tb1 ORF); in blue, primers used to genotype the \emph{Hopscotch} insertion.}
  \end{center}
\end{figure*}
%-------------------------------------------------------------------

\clearpage
\pagenumbering{arabic}
\chead{\small{Vann et al.---American Journal of Botany (\#\#)(\#): \#\#\#-\#\#\#. 2014. -- Appendix S4 -- Page \thepage}}

% Appendix S4. Gel image
%-------------------------------------------------------------------
\begin{figure*}[!t]
  \begin{center}
   \includegraphics[width=100mm]{FigS2Gel.png}
   \flushleft{Appendix S4: Agarose gel image of amplification products using our primer sets. Genotypes are indicated at the top of the gel.} 
  \end{center}
\end{figure*}
%-------------------------------------------------------------------

\clearpage
\pagenumbering{arabic}
\chead{\small{Vann et al.---American Journal of Botany (\#\#)(\#): \#\#\#-\#\#\#. 2014. -- Appendix S5 -- Page \thepage}}

% Appendix S5. NJ Trees
%-------------------------------------------------------------------
\begin{figure*}[!t]
  \begin{center}
   \includegraphics[width=150mm]{FigS3NJtrees.pdf}
    \flushleft{Appendix S5: Neighbor-joining tree of the sequenced region in the 5' UTR (right; Region 1) and the 66,169 bp upstream region (left; Region 2) of \emph{tb1}. Individuals with genotype data are colored: Homozygous for the teosinte (no \emph{Hopscotch}) allele (red), homozygous for the maize (\emph{Hopscotch}) allele (blue), heterozygotes (purple). TILs (teosinte inbred lines) are colored in green, with stars indicating the 3 TILs known to have the \emph{Hopscotch} insertion. Black indicates individuals not genotyped for the \emph{Hopscotch} insertion.} 
  \end{center}
\end{figure*}
%-------------------------------------------------------------------
\end{document}
